---
title: "r4ds 8"
author: "Jihye"
date: "3/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dbplyr)
library(tidyverse)
library(stringr)
library(statar)
library(microbenchmark)
library(lubridate)
library(jsonlite)
library(ggmap)
library(maps)
library(RMySQL)
```
#1 Chapter 21

1. 
```{r}
# mean
mean <- vector("double", ncol(mtcars))
for (i in seq_along(mtcars)) {
  mean[[i]] <- mean(mtcars[[i]])
}


#type
type <- vector("character", ncol(nycflights13::flights))
for (i in seq_along(nycflights13::flights)) {
  type[[i]] <- typeof(nycflights13::flights[[i]])
}


#unique value
unique_value <- vector("double", ncol(iris))
for (i in seq_along(iris)) {
  unique_value[[i]] <- n_distinct(iris[[i]])
}


#random normal
vector <- c(-10, 0, 10, 100)
random_norm <- data.frame(matrix(NA, ncol = 4, nrow = 10))
for (i in seq_along(vector)) {
  random_norm[[i]] <- rnorm(10, mean = vector[[i]])
}

mean
type
unique_value
random_norm
```    


2.
```{r}

out <- ""
for (x in letters) {
  out <- stringr::str_c(out, x)
}
out

# an existing function
str_c(letters, collapse = "")


x <- sample(100)
sd <- 0
for (i in seq_along(x)) {
  sd <- sd + (x[i] - mean(x)) ^ 2
}
sd <- sqrt(sd / (length(x) - 1))

# an existing function
sd(x)


x <- runif(100)
out <- vector("numeric", length(x))
out[1] <- x[1]
for (i in 2:length(x)) {
  out[i] <- out[i - 1] + x[i]
}


# an existing function
cumsum(100)
```     


3.
```{r}
number_vector <- c("ten", "nine", "eight", "seven", "six", "five",
             "four", "three", "two", "one")
for (i in number_vector) {
  print(c("There were",i,"in the bed"))
  print("and the little one said")
  print("'Roll over, roll over'")
  print("So they all rolled over and one fell out")
}
```

4.
```{r}

# from the pset

#output <- vector("integer", 0) 
#for (i in seq_along(x)) {
#  output <- c(output, lengths(x[[i]]))
#}
#output


#sample test
f1 <- function (n) {
    list <- list()
    for(i in 1:n) {
        list <- append(list, i)
    }
    return(list)
}

f2 <- function (n) {
    list <- list()
    for(i in 1:n) {
        list[[length(list) + 1]] <- i
    }
    return(list)
}
microbenchmark(f1(30000), times = 3)
microbenchmark(f1(30000), times = 3)
```
secone one is faster by 0.14 second.    

5.
```{r}
files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)
df <- vector("character", length(files))
for (file in seq_along(files)) {
  df[[i]] <- read_csv(files[[i]])
}
df <- bind_rows(df)
```

6.
```{r}
show_mean <- function(df) {
  for (i in seq_along(df)) {
    if (is.numeric(df[[i]])) {
      cat(str_c(names(df[i]), round(mean(df[[i]]), 2), sep = " - "),
          "\n")
    }
  }
}

show_mean(iris)
```

7. The code lists two variables, disp and am. 
disp is the value multiplied by 0.0163871 and 
am is a factor variable with the value either auto ot manual.  

```{r}
trans <- list( 
  disp = function(x) x * 0.0163871,
  am = function(x) {
    factor(x, labels = c("auto", "manual"))
  }
)
for (var in names(trans)) {
  mtcars[[var]] <- trans[[var]](mtcars[[var]])
}
```


8.
```{r}
col_summary <- function(df, fun) {
  out <- vector("double", length(df))
  for (i in seq_along(df)) {
    out[i] <- fun(df[[i]])
  }
  out
}
```

9.
```{r }
# the mean of every column in mtcars.
#map_dbl(mtcars, mean)

#the type of each column in nycflights13::flights.
map_chr(nycflights13::flights, typeof)

#the number of unique values in each column of iris.
map_int(iris, n_distinct)

#10 random normals for each of ?? = ???10, 0, 10, and 100.
vector <- c(-10, 0, 10, 100)
#map(vector, rnorm, n = 10)

```

10.
```{r}
map_lgl(nycflights13::flights, is.factor)
```

None of the columns in the flights dataframe are made up of factors.

11.
```{r warning = FALSE, message = FALSE, error = TRUE}
map(1:5, runif)
map(-2:2, rnorm, n = 5)
map_dbl(-2:2, rnorm, n = 5)
```
The last one gives the error: "Result 1 is not a length 1 atomic vector"

#2 Chapter 28

1. 
```{r}
ggplot(mpg) +
  geom_point(aes(x = displ, y = hwy, color = trans)) +
  labs(x = "displacement",
       y = "highway miles per gallon",
       color = "transmission",
       title = "fuel efficiency",
       subtitle = "mpg dataset",
       caption = "data from year xxxx")
```

2.
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = class)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs( x = "displacement",
    y = "mpg",
    colour = "type",
    title = "fuel efficiency by car size",
   caption = "data from year xxxx")
```

4. You can add text at any point in a plot. You only need to have the proper coordinates for where you want your text to be.
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  annotate("text", x = 6, y = 40, label = "yesssss")
```

6. The four arguments for arrow within geom_segment are:

angle : angle of arrow head  
length : length of the arrow head 
ends: ends of the line
type: whether the arrow head is closed or open

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() + 
  geom_segment(aes(x = 7, y = 30, xend = 5.5, yend = 6, colour = "segment"),
               arrow = arrow(angle = 30, length = unit(0.5, "cm"),
                             ends = "first", type = "open")
               )
```

7.
```{r}
year <- make_date(seq(year(min(presidential$start)),
                      year(max(presidential$end)),
                      by = 4), 1, 1
                  )

presidential %>%
  mutate(id = 33 + row_number(),
         name_id = str_c(name, "-", id)) %>%
  ggplot(aes(x = start, y = name_id, colour = party)) +
  geom_point() +
  geom_segment(aes(xend = end, yend = name_id)) +
  scale_colour_manual(values = c(Republican = "red", Democratic = "blue")) +
  scale_x_date(NULL, breaks = year, date_labels = "%Y") 

```

8.
```{r}

ggplot(diamonds, aes(carat, price)) +
  geom_point(aes(colour = cut), alpha = 1/20) +
   guides(colour = guide_legend(nrow = 1, override.aes = list(alpha = 1)))  

```








